\vspace{-0ex}Bench: Evaluating Arbitrary Workloads

### 2017-12-10 paper/submission.tex
Added Distributed Architecture back.

\section{Design}
In this section, we explain the design choices made for \textit{bench}. We argue that these design choices allow \textit{bench} to benchmark most if not all types of workloads.

By using a probability distribution for tasks and an exponential distribution for arrival time, along with a simulated distributed environment, \textit{bench} is capable of modelling most industrial workloads.

@@

Consider a workload which processes I/O tasks with a very strict order. A random read in this workload is followed by a sequential write, which is then followed by a random read and so on. While it is possible to benchmark such a workload through a probability distribution, a benchmark based solely on task distribution will be inaccurate as it will not be able to guarentee the order of the tasks. Future version of \textit{bench} aim to find a workaround.

@@

\subsection{Distributed Architecture}

\section{Implementation}
want it to be easy to sue and flexible. something something parametrization...benchmark engine....C...

>>>>

\section{Design}
We have designed \textit{bench} with keeping this background in mind. In this section, we explain the design choices made for \textit{bench}. We argue that these design choices allow \textit{bench} to benchmark most if not all types of workloads. By using a probability distribution for tasks and an exponential distribution for arrival time, along with a simulated distributed environment, \textit{bench} is theoretically capable of modelling most industrial workloads.

@@

Consider a workload which processes I/O tasks with a very strict order. A random read in this workload is followed by a sequential write, which is then followed by a random read and so on. While it is possible to benchmark such a workload through a probability distribution, a benchmark based solely on task distribution will be inaccurate as it will not be able to guarentee the order of the tasks. Future versions of \textit{bench} aim to find a workaround.

@@

\subsection{Distributed Architecture}
Most industrial applications are built as distributed systems which divide work amongst different entities in order to better process requests from clients. In a generic distributed application, a frontend system collects a request from a user and forwards it to a backend system. This backend system processes this request and ships the information back to the frontend or to the client.

The reason this system is as such is because industrial applications operate at a huge scale and service thousands of requests at a given time. It is simply not possible for a single machine to keep up with the incoming requests from impatient clients. For a system such as this, the main bottleneck used to be the latency of network connections which connected the frontend to the backend. However, with advances in network technology and the introduction of standards such as \textbf{Infiniband} \cite{}, this is not true anymore. Instead, the main bottleneck for these systems is the storage media, which operate at a fraction of the speed of CPU and RAM.

As the network is not a bottleneck anymore, we decided that we can combine the frontend and the backend into a single application and simulate them using threads instead of building two separate applications, one for the frontend and one for the backend, and then connect them together using a network simulator. We claim that having two separate applications because of something which as is does not limit performance provides no benefit to having an application which simulates entities using threads. Infact, we argue that bulding separate applications leads to more bug prone software and will overall provide deprecating results.

Moreover, we decided that a single instance of \textit{bench} will only benchmark a single workload. We pin each entity to its own thread and so benchmarking multiple workloads simply means more threads. As the relative overhead of setting up an entity is small, having separate instances represent different workloads is not any more costlier and provides a cleaner, more manageable design.

\section{Implementation}
Our goal was to make \textit{bench} an easy to use and flexible application. As \textit(bench) requires heavy parametrization due to its design, we decided that the best way to bu
want it to be easy to sue and flexible. something something parametrization...benchmark engine....C...
